Characterizing hippocampal replay using hybrid point process state space models

### 2019-11-30 paper.tex
Updates from Overleaf

\begin{figure}[t]
\centerline{\includegraphics{fig1.pdf}}
\caption{The framework can be used to characterize changes between spatially continuous and spatially fragmented replay trajectories on simulated and real data. \textbf{(a)} The left plot shows a replay from 19 simulated neurons, arranged by the peak of their place fields, where the first three quarters of the replay is simulated to be spatially continuous and the last quarter is spatially fragmented. The black ticks indicate times when an action potential occurred. The blue and orange lines indicate the estimated probability of the continuous and fragmented discrete states over time $Pr(I_{k} \mid \Delta N_{1:T}^{(1:C)}, H_{k})$, respectively. The right plot shows the posterior probability of position represented by the neurons over time, marginalized over the discrete states $p(x_{k} \mid \Delta N_{1:T}^{(1:C)}, H_{k})$. \textbf{(b)} An example of how the model can capture similar patterns in real data from the spiking patterns of 32 hippocampal neurons during a sharp wave ripple. Conventions are the same as in the first plot. Positions in the right plot correspond to linearized position of a W-shaped track, where 0 cm corresponds to the top of the middle tine of the W, 354 cm corresponds to the top of the left tine of the W, and 212 cm corresponds to the right tine of the W. The top of the center arm and bottoms of the left and right arm are connected.}
\label{fig1}
\end{figure}

@@

\section*{Acknowledgments}
\printbibliography
\end{document}

>>>>

\begin{figure}[t]
\centerline{\includegraphics{fig1.pdf}}
\caption{The framework can be used to characterize changes between spatially continuous and spatially fragmented replay trajectories on simulated and real data. \textbf{(a)} The left plot shows a replay from 19 simulated neurons, arranged by the peak of their place fields, where the first three quarters of the replay is simulated to be spatially continuous and the last quarter is spatially fragmented. The black ticks indicate times when an action potential occurred. The blue and orange lines indicate the estimated probability of the continuous and fragmented discrete states over time $Pr(I_{k} \mid \Delta N_{1:T}^{(1:C)}, H_{k})$, respectively. The right plot shows the posterior probability of position represented by the neurons over time, marginalized over the discrete states $p(x_{k} \mid \Delta N_{1:T}^{(1:C)}, H_{k})$. \textbf{(b)} An example of how the model can capture similar patterns in real data from the spiking patterns of 32 hippocampal neurons during a SWR. Conventions are the same as in the first plot for the left plot. Positions in the right plot correspond to linearized position of a W-shaped track. The 2D representation of the W-shaped track is shown at the bottom center of the figure. Colored arrows indicate the corresponding arm and alignment with the linear axis. L, R, C demarcate the left arm, right arm, and center arm respectively.}
\label{fig1}
\end{figure}

@@

\printbibliography
\end{document}
